---
title: "My Data Dashboard"
output: 
  flexdashboard::flex_dashboard: 
  vertical_layout: fill
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("HelpMe.r")
library(zoo)
library(patchwork)
library(DT)
library(plotly)
library(tidyverse)
library(lubridate)
library(timetk)
library(scales)
library(devtools)
library(googlesheets4)
library(rio)
library(flexdashboard)
```

```{r, include=FALSE}
sheets_df <- read_sheet('https://docs.google.com/spreadsheets/d/1T5aBqYKlqTwXyZZQXrihkfNxLuKONRJomhFlTL6id4k/edit#gid=1028012845', "DataForR")

```


```{r, include=FALSE}
fulldf <-  sheets_df %>% 
mutate(
chronic_sRPE = rollmean(sRPE, k = 28, align = "right", na.pad = T ),
acute_sRPE = rollmean(sRPE, k = 7, align = "right", na.pad = T),
chronic_HRV = rollmean(HRV, k = 28, align = "right", na.pad = T ),
acute_HRV = rollmean(HRV, k = 7, align = "right", na.pad = T),
chronic_RHR = rollmean(RHR, k = 28, align = "right", na.pad = T ),
acute_RHR = rollmean(RHR, k = 7, align = "right", na.pad = T),
rolling_energy = rollmean(Energy, k = 14, align = "right", na.pad = T),
rolling_sore = rollmean(Soreness, k = 14, align = "right", na.pad = T))

fulldf = fulldf %>%
mutate(
ACWR = acute_sRPE / chronic_sRPE, digits = 2) %>%
mutate(Date2 = ydm(Date)) 

summarized180 <- fulldf %>%
mutate(Date2 = ymd(Date)) %>%
filter(between(Date2, today() - days(180), today() )) %>%
rename(DateOld = Date) %>%
rename(Date = Date2) %>%
drop_na() %>%
summarize(
HRV_avg = mean(HRV),
HRV_sd = sd(HRV),
RHR_avg = mean(RHR),
RHR_sd = sd(RHR))

summarized180 <- summarized180 %>%
mutate(
HRV_top = HRV_avg + HRV_sd,
HRV_bottom = HRV_avg - HRV_sd,
RHR_top = RHR_avg + RHR_sd,
RHR_bottom = RHR_avg - RHR_sd)
```

Overview 
==============================

Column {data-width = 600}
------------


### **WORKLOAD + WELLNESS OVERVIEW**
```{r, include=FALSE}
fulldf

last60 <-  fulldf %>%
drop_na(RHR, RHR) %>%
mutate(Date2 = ymd(Date)) %>%
filter(between(Date2, today() - days(60), today() )) %>%
rename(DateOld = Date) %>%
rename(Date = Date2) %>%
mutate(
HRV_top = summarized180$HRV_top,
HRV_bottom = summarized180$HRV_bottom,
RHR_top = summarized180$RHR_top,
RHR_bottom = summarized180$RHR_bottom)

sRPEplot <- ggplot(data = last60) + 
geom_area(aes(x = Date, y = chronic_sRPE), fill = "#00CC00", alpha = 0.2, color = "#33FF00") +
geom_line(aes(x = Date, y = chronic_sRPE), color = "#00CC00", size = 1) +
geom_col(aes(x = Date, y = sRPE), fill = "#FFCC33", color = "transparent") + 
ylab("sRPE")+
xlab(element_blank())+
ggtitle("Session RPE") +
theme(plot.title = element_text(size = 18)) + 
theme_minimal()

HRVplot <- ggplot(data = last60) + 
geom_line(aes(x = Date, y = HRV), color = "#663366", size = 1.5) +
geom_point(aes(x = Date, y = HRV), fill = "#663366", color = "#330066", size = 2) + 
ylab("HRV")+
geom_line(aes(x = Date, y = HRV_bottom), color = "blue", size = 1, linetype = "dashed", alpha = 0.5) +
geom_line(aes(x = Date, y = HRV_top), color = "red", size = 1, linetype = "dashed", alpha = 0.5) + 
xlab(element_blank())+
ggtitle("HRV") +
theme(plot.title = element_text(size = 18)) + 
theme_minimal() +
ylim(20,60)

RHRplot <- ggplot(data = last60) + 
geom_line(aes(x = Date, y = RHR), color = "#FF6666", size = 1.5) +
geom_point(aes(x = Date, y = RHR), fill = "#CC0000", color = "#CC0000", size = 2) + 
ylab("RHR")+
geom_line(aes(x = Date, y = RHR_bottom), color = "blue", size = 1, linetype = "dashed", alpha = 0.5) +
geom_line(aes(x = Date, y = RHR_top), color = "red", size = 1, linetype = "dashed", alpha = 0.5) + 
xlab(element_blank())+
theme_minimal() + 
ggtitle("RHR") +
theme(plot.title = element_text(size = 14)) + 
ylim(40,60)

sRPEplotly <-  ggplotly(sRPEplot)
HRVplotly <- ggplotly(HRVplot)
RHRplotly <- ggplotly(RHRplot)

```

```{r fig.width = 12, fig.height= 12, echo=FALSE}
sRPEplotly
```


Column {data-width = 400}
------------
###

```{r fig.width = 12, fig.height= 12, echo=FALSE}
HRVplotly
```

###

```{r fig.width = 12, fig.height= 12, echo=FALSE}
RHRplotly
```

------------

This Week
==============================

Column{.tabset}
---------------------

### **Energy**

```{R, echo = FALSE}
last7wellness <- fulldf %>%
  mutate(Date2 = ymd(Date)) %>%
  rename(OldDate = Date) %>%
  rename(Date = Date2) %>%
  rename(OldSleep = Sleep) %>%
  rename(Sleep = `Sleep (hrs)`) %>%
  filter(between(Date, today() - days(6), today()))

ggplotly(ggplot(last7wellness, aes(x = Date, y = Energy)) + 
  geom_line(aes(y = rolling_energy), color = "black", size = 1.5, linetype = 'dashed') + 
  geom_col(fill = "#FFCC33") +
  ylim(0,10) +
  ylab(element_blank()) +
  xlab(element_blank()) +
  ggtitle("Energy") +
  theme(plot.title = element_text(size = 18)) + 
  theme_ipsum())
```

### **Soreness**

```{R, echo = FALSE}
ggplotly(ggplot(last7wellness, aes(x = Date)) + 
  geom_line(aes(y = rolling_sore), color = "grey", size = 1.5, linetype = 'dashed') +
  geom_col(aes(y = Soreness), fill = "#000222") +
  ylim(0,10) +
  ylab(element_blank()) +
  xlab(element_blank()) +
  ggtitle("Soreness") +
  theme(plot.title = element_text(size = 18)) + 
  theme_ipsum())

```


### **RHR**
```{R, echo = FALSE}

ggplotly(ggplot(last7wellness, aes(x = Date, y = RHR)) + 
  geom_area(fill = "#FF6666", alpha = 0.5) +
  geom_line(color = "#CC0000", size = 1.5) +
  geom_point(color = "#FF6666", size = 3) +
  ylab(element_blank()) +
  xlab(element_blank()) +
  ggtitle("RHR") +
  theme(plot.title = element_text(size = 18)) + 
  theme_ipsum())
```

### **HRV**

```{R, echo = FALSE}

ggplotly(ggplot(last7wellness, aes(x = Date, y = HRV)) + 
  geom_area(color = "#663366", alpha = 0.5) +
  geom_line(color = "#330066", size = 1.5) +
  geom_point(color = "#663366", size = 3) +
  ylab(element_blank()) +
  xlab(element_blank()) +
  ggtitle("HRV") +
  theme(plot.title = element_text(size = 18)) + 
  theme_ipsum())

```

Column
------------------------

### **7-Day Table**

```{r fig.width= 8, echo= FALSE}
last7table <- fulldf %>%
  mutate(Date2 = ymd(Date)) %>%
  rename(OldDate = Date) %>%
  rename(Date = Date2) %>%
  rename(OldSleep = Sleep) %>%
  rename(Sleep = `Sleep (hrs)`) %>%
  select(Date, HRV, RHR, sRPE, ACWR) %>%
  filter(between(Date, today()-days(7), today())) %>%
  arrange(desc(Date))

last7table$ACWR <- format(last7table$ACWR, digits = 2)
last7table$Date <- weekdays(last7table$Date)

datatable(last7table, rownames = FALSE)
